Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-26 papers/actus2021/article.tex
Typos

\noindent 
\begin{equation*}
\ident{state}_{i}=\ident{path}_{i}(\ident{INIT}(ct)),
\end{equation*}
\noindent
where \emph{ct} stands for contract terms, \emph{INIT} returns initial state, \emph{sched}
returns scheduled events, \emph{STF} takes \emph{contract terms}, \emph{event}, and \emph{state}
and returns the next state, and \emph{POF} returns the \emph{payoff} from a state.

>>>>

\noindent 
\begin{equation*}
\ident{state}_{i}=\ident{path}_{i}(\ident{INIT}(ct)),
\end{equation*}
\noindent
where \emph{ct} stands for contract terms, \emph{INIT} returns initial state, \emph{sched}
returns scheduled events, \emph{STF} takes \emph{contract terms}, \emph{event}, and \emph{state}
and returns the next state, and \emph{POF} returns the \emph{payoff} in a state.
